\chapter{\REVIEW{Functional Overview}}
\label{chap:functional-overview}

This chapter provides an overview of the functional requirements for the hidden speed camera.
The system consists of a SoC (system on a chip) and a camera.
It detects the speed of vehicles by making use of the camera footage, and then uses ALPR (Automatic License Plate Recognition) to get the license plate.
Both the speed detection and ALPR will be done by making use of computer vision.

\section{General}

\begin{itemize}
    \item {[FUN\_GEN\_001]}: The system fits in a garbage bin.
    \item {[FUN\_GEN\_002]}: The system boots up autonomously and is operational within 30 seconds.
    \item {[FUN\_GEN\_003]}: The system detects vehicles in both directions. (Could have)
\end{itemize}

\subsection{System on a chip}

\begin{itemize}
    \item {[FUN\_SOC\_001]}: The system locally stores pictures of the vehicles of speeding road users.
    \item {[FUN\_SOC\_002]}: The system locally stores pictures of the license plates of speeding road users.
    \item {[FUN\_SOC\_003]}: The system keeps all pictures for a minimum of 30 days.
\end{itemize}

\subsection{License Plate Recognition}

\begin{itemize}
    \item {[FUN\_LPR\_001]}: The system recognizes Dutch and Belgian license plates under the following conditions:
    \begin{itemize}
        \label{iss:lighting}
        \item Unobscured image of the entire license plate
        \item Good lighting conditions
    \end{itemize}
\end{itemize}

\subsection{Speed Detection}

\begin{itemize}
    \item {[FUN\_SPE\_001]}: The system measures vehicle speeds with a maximum deviation of 10\% or 5 km/h.
\end{itemize}

\section{Interfaces}

\subsection{WiFi}

The user can configure the speed camera and access its files by connecting to its WiFi network.

\begin{itemize}
    \item {[FUN\_WIF\_001]}: The system create a WiFi accesspoint to which the client can connect.
    \item {[FUN\_WIF\_001]}: The system hosts a HTTP web server through which the user can download footage and configure the speed camera.
\end{itemize}

\subsection{Camera}

The camera interface will be determined after the research is completed.
