\chapter{\REVIEW{Development Board Comparison}}
\label{app:board-comparison}

\section{Hardware}

\cref{tbl:board-comparison} shows the differences in hardware between the Jetsen Nano Developer Kit and the Raspberry Pi 4.
These board have many similarities in hardware. They are both equipped with an ARM CPU (Central Processing Unit) and 4 GB of LPDDR4 (Low-Power Double Data Rate) memory.
The biggest difference between these board is that the RPI 4 has an Broadcom VideoCore VI, and the Jetson Nano has a much more powerful 128-core Maxwell GPU (Graphics Processing Unit).

\begin{lintable}{tbl:board-comparison}{Board Hardware Comparison}
    \begin{lintabular}{l|l|l}
        \lintablehead{       & Jetson Nano Developer Kit    & Raspberry Pi 4}
        \lintablerow{CPU     & Quad-core ARM A57 @ 1.43 GHz & Quad-core ARM Cortex-A72 @ 1.5 GHz}
        \lintablerow{Memory  & 4 GB 64-bit LPDDR4 25.6 GB/s & 4 GB LPDDR4-3200}
        \lintablerow{GPU     & 128-core Maxwell             & Broadcom VideoCore VI}
        \lintablerow{Camera  & 2x MIPI CSI-2 DPHY lanes     & 2-lane MIPI CSI camera port}
    \end{lintabular}
\end{lintable}

The data in this table is retrieved from \cite{nvidia:jetson-nano-datasheet} and \cite{rpiltd:raspberry-pi-datasheet}.

\cref{tbl:gpu-comparison} displays the difference between the GPUs.
You can see that the Maxwell GPU has around 8 times better performance then the VideoCore VI.

\begin{lintable}{tbl:gpu-comparison}{GPU Comparison}
    \begin{lintabular}{l|l|l}
        \lintablehead{                   & 128-core Maxwell & Broadcom VideoCore VI}
        \lintablerow{Performance (GLOPS) & 512              & 64}
        \lintablerow{Clock speed (MHZ)   & 921              & 500}
    \end{lintabular}
\end{lintable}

The data in this table is retrieved from \cite{nvidia:jetson-nano-datasheet} and \cite{gdgtvs:videocore-vi-benchmark}.

\section{Interfaces}
\label{sec:board-comparison-interfaces}

As shown in \cref{tbl:board-comparison}, both devices support MIPI CSI-2 (Camera Serial Interface).
Both device also have a Gigabit Ethernet port. However, the RPI 4 also has 802.11 b/g/n/ac Wireless LAN and the Jetson Nano does not.
